---
title: "jv2629_hw6"
author: "Jaclyn Verity - jv2629"
date: "November 27, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(RCurl)
library(modelr)
```

#Introduction
This document is to practice using linear models and graphing them for the Data Science Course HW 6.

#Problem 1

**Load the data.**
```{r}
require(RCurl)
hom_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```

**Clean the data.**
```{r}
hom_clean = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 1, 0))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
   mutate(victim_race = as.factor(ifelse(victim_race == "White", "white", "non-white" )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white", "non-white"))

```

**Run a GLM Model for Baltimore.**

```{r}
hom_balt = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 'solved', 'unsolved'))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(victim_race = as.factor(ifelse(victim_race == "White", "white", "non-white" )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white", "non-white"))

balt_outcomes = hom_balt %>% 
   glm(outcome ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate*1.96 - std.error),
         high_OR = exp(estimate*1.96 + std.error)) %>%
  select(OR, low_OR, high_OR, p.value) %>% 
  knitr::kable(digits = 3)
```

Creating a function for running glm and pulling it into a table.
```{r}
hom_glm = hom_clean %>% 
  select(city_state, victim_race, victim_age, victim_sex, outcome)

glm_resolv_func = function(df){
  
 glm(df$outcome ~ df$victim_age + df$victim_race + df$victim_sex, data = df, family = binomial()) %>% 
    broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate - (1.96 * std.error)),
         high_OR = exp(estimate + (1.96 * std.error))) %>%
  select(term, OR, low_OR, high_OR)
}
```

Run function and create data frame.
```{r}
hom_nest = nest(hom_glm, victim_race:outcome)

or_outcomes = hom_nest %>% 
  mutate(glm_out =
    map(hom_nest$data, glm_resolv_func)) %>% 
  select(-data) %>% 
  unnest() %>% 
  janitor::clean_names()
```

Plot of victim race for each city. 
```{r}
race_plot = or_outcomes %>% 
  filter(term == "df$victim_racenon-white")

race_plot %>% 
  mutate(city_state = fct_reorder(city_state, or)) %>% 
ggplot(aes(x = city_state, y = or)) +
  coord_flip() +
  geom_point() + 
  geom_errorbar(aes(ymin = low_or, ymax = high_or)) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1)) +
  labs(x = "City", y = "Odds of Solved Murder based on Race (White v Non-White)")
```

#Problem 2

**Load and clean data set for analysis on birthweight.**
```{r}
raw_birth = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names()
```

A number of studies have researched what influences a baby's birthweight. From my experience with the literature I am selecting:
- ppbmi = mother's pre pregnancy bmi (pounds)
- gaweeks = gestational age (weeks)
- smoken = average number of cigarettes smoked per day during pregnancy

A mother's pre pregnancy bmi has been shown to incease a babys birthweight by 37 grams for every 1 unit increase in bmi. Baby's meet milestones for development and weight at certain ages of gestation, it's age at birth will be related to birth weight. Smoking has also been shown to affect babies development which will affect the birth weight. 

**Clean data for linear regressions.**
```{r}
clean_birth = raw_birth %>% 
  select(blength, bwt, bhead, babysex, ppbmi, gaweeks, smoken) %>% 
  mutate(babysex = as.factor(babysex))

na.omit(clean_birth)
```


