---
title: "jv2629_hw6"
author: "Jaclyn Verity - jv2629"
date: "November 27, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(RCurl)
```

#Introduction
This document is to practice using linear models and graphing them for the Data Science Course HW 6.

#Problem 1

**Load the data.**
```{r}
require(RCurl)
hom_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```

**Clean the data.**
```{r}
hom_clean = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 'solved', 'unsolved'))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
  mutate(victim_race = as.factor(ifelse(victim_race == 'White', 'white', 'non-white' )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white"))

```

**Run a GLM Model for Baltimore.**

```{r}
hom_balt = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 'solved', 'unsolved'))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(victim_race = as.factor(ifelse(victim_race == 'White', 'white', 'non-white' )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white"))

balt_outcomes = hom_balt %>% 
   glm(outcome ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate*1.96 - std.error),
         high_OR = exp(estimate*1.96 + std.error)) %>%
  select(OR, low_OR, high_OR, p.value) %>% 
  knitr::kable(digits = 3)
```

Creating a function for running glm and pulling it into a table.
```{r}
hom_glm = hom_clean %>% 
  select(city_state, victim_race, victim_age, victim_sex, outcome)

glm_resolv_func = function(df){
  
 glm(df$outcome ~ df$victim_age + df$victim_race + df$victim_sex, data = df, family = binomial()) %>% 
    broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate*1.96 - std.error),
         high_OR = exp(estimate*1.96 + std.error)) %>%
  select(OR, low_OR, high_OR, p.value) %>% 
  knitr::kable(digits = 3)
}
```



hom_nest = nest(hom_glm, victim_race:outcome)

or_outcomes = hom_nest %>% 
  mutate(glm_out =
    map(hom_nest$data, glm_resolv_func)) %>% 
  select(-data) %>% 
  unnest() %>% 
  janitor::clean_names()
  
```

