---
title: "jv2629_hw6"
author: "Jaclyn Verity - jv2629"
date: "November 27, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(RCurl)
library(modelr)
library(mgcv)
```

#Introduction
This document is to practice using linear models and graphing them for the Data Science Course HW 6.

#Problem 1

**Load the data.**
```{r}
require(RCurl)
hom_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```

**Clean the data.**
```{r}
hom_clean = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 1, 0))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
   mutate(victim_race = as.factor(ifelse(victim_race == "White", "white", "non-white" )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white", "non-white"))

```

**Run a GLM Model for Baltimore.**

```{r}
hom_balt = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', '),
         outcome = as.factor(ifelse(disposition == 'Closed by arrest', 'solved', 'unsolved'))) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(victim_race = as.factor(ifelse(victim_race == "White", "white", "non-white" )),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white", "non-white"))

balt_outcomes = hom_balt %>% 
   glm(outcome ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate*1.96 - std.error),
         high_OR = exp(estimate*1.96 + std.error)) %>%
  select(OR, low_OR, high_OR, p.value) %>% 
  knitr::kable(digits = 3)

balt_outcomes
```

Creating a function for running glm and pulling it into a table.
```{r}
hom_glm = hom_clean %>% 
  select(city_state, victim_race, victim_age, victim_sex, outcome)

glm_resolv_func = function(df){
  
 glm(df$outcome ~ df$victim_age + df$victim_race + df$victim_sex, data = df, family = binomial()) %>% 
    broom::tidy() %>% 
  mutate(OR = exp(estimate),
         low_OR = exp(estimate - (1.96 * std.error)),
         high_OR = exp(estimate + (1.96 * std.error))) %>%
  select(term, OR, low_OR, high_OR)
}
```

Run function and create data frame.
```{r}
hom_nest = nest(hom_glm, victim_race:outcome)

or_outcomes = hom_nest %>% 
  mutate(glm_out =
    map(hom_nest$data, glm_resolv_func)) %>% 
  select(-data) %>% 
  unnest() %>% 
  janitor::clean_names()
```

Plot of victim race for each city. 
```{r}
race_plot = or_outcomes %>% 
  filter(term == "df$victim_racenon-white")

race_plot %>% 
  mutate(city_state = fct_reorder(city_state, or)) %>% 
ggplot(aes(x = city_state, y = or)) +
  coord_flip() +
  geom_point() + 
  geom_errorbar(aes(ymin = low_or, ymax = high_or)) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1)) +
  labs(x = "City", y = "Odds of Solved Murder based on Race (White v Non-White)")
```

#Problem 2

**Load and clean data set for analysis on birthweight.**
```{r}
raw_birth = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names()
```

A number of studies have researched what influences a baby's birthweight. From my experience with the literature I am selecting:
- ppbmi = mother's pre pregnancy bmi (pounds)
- gaweeks = gestational age (weeks)
- smoken = average number of cigarettes smoked per day during pregnancy

A mother's pre pregnancy bmi has been shown to incease a babys birthweight by 37 grams for every 1 unit increase in bmi. Baby's meet milestones for development and weight at certain ages of gestation, it's age at birth will be related to birth weight. Smoking has also been shown to affect babies development which will affect the birth weight. 

**Clean data for linear regressions.**
```{r}
clean_birth = raw_birth %>% 
  select(blength, bwt, bhead, babysex, ppbmi, gaweeks, smoken) %>% 
  mutate(babysex = as.factor(babysex))

na.omit(clean_birth)
```

**Modeling.**
```{r}
fit = lm(bwt ~ ppbmi + gaweeks + smoken, data = clean_birth)

fit %>% broom::glance()
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

**Plot residuals against predictions.**
```{r}
clean_birth %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point()
```

**Compare my model to other models.**

Length and gestational age.
```{r}
fit1 = lm(bwt ~ blength + gaweeks, data = clean_birth)
fit1 %>% broom::glance()
fit1 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

My models r squared value is 0.185 which indicates that my model can explain 18.5% of the variance we see in birth weight. The length and gestational age model has an r squared value of 0.577 so 57.7% of the variation in birth weight is explained by this model. 


Head circumfrence, baby sex, and length at birth.
```{r}
fit2 = lm(bwt ~ bhead + blength + babysex + (bhead*blength) + (bhead*babysex) + (blength*babysex) + (bhead*blength*babysex), data = clean_birth)
fit2 %>% broom::glance()
fit2 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

My models r squared value is 0.185 which indicates that my model can explain 18.5% of the variance we see in birth weight.The length, head circumfrence, and baby sex model has an r squared value of 0.685 so 68.5% of the variation in birth weight is explained by this model.

**Create cross validation.**
```{r}
set.seed(216)
cv_birth = crossv_mc(clean_birth, 100)
cv_birth = 
  cv_birth %>% 
  mutate(
    my_mod = map(train, ~fit),
    mod1 = map(train, ~fit1),
    mod2 = map(train, ~fit2)) %>% 
  mutate(rmse_my_mod    = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)))
```

**Plot RMSE.**
```{r}
cv_birth %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

The plot shows the root mean square errors (RMSE) for my model and the two comparison models. My model has a (RMSE) of about 460, Model 1 RMSE = 340, and Model 2 = 280. The RMSE is a measure of the unexplained variance and if it is low then the model does not have a wide range of unexplained variance. Model 2 (the model with head circumfrence, length, sex, and the interactions) is the best model with the smallest RMSE.